Ecological network control

### 2018-06-17 paper/manuscript.Rmd
Use references in submodule

---
title: "Working title: Ecological network control"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: references.bib
---

>>>>

---
title: "Working title: Ecological network control"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

### 2018-06-17 paper/supp-info.Rmd
Use references in submodule

---
title: "Ecological network control"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
bibliography: references.bib
---

>>>>

---
title: "Ecological network control"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
  - \usepackage{multirow}
bibliography: phd-bibliography/network-control.bib
---
